%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Sarthak Grover
\documentclass[margin,line]{resume}

\usepackage[svgnames]{xcolor}
\PassOptionsToPackage{cmyk}{xcolor}
%\usepackage{hyperref}
\usepackage[pdftex,bookmarks=true]{hyperref}
%\usepackage[T1]{fontenc}
%\usepackage{ae,aecompl}

\definecolor{hyperblue}{HTML}{191940}

\hypersetup{
  colorlinks = true,
  urlcolor = hyperblue,
  pdfpagemode = UseNone
}

%\setcounter{secnumdepth}{-1}

%______________________________________________________________________________________________________________________
\begin{document}
\name{\huge{\sc {Sarthak Grover}} \hspace{4.33in} \small{\emph{PhD. Student}} \vspace{4pt}}
\begin{resume}

    %__________________________________________________________________________________________________________________
%     % Optional
%     \section{} {\vspace{-1pt}\scriptsize {\sc B.Tech $|$ Electronics and Communication $|$ M.Tech $|$ Wireless Communication $|$ IIT Roorkee}}
% 
    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle \normalsize Contact\\Information}

    \href{http://gtnoise.net/}{Network Operations and Internet Security Lab}	\\
    School of Computer Science    \hfill \emph{Phone:} (408) 220-5735\\
    \href{http://www.gatech.edu/}{Georgia Institute of Technology}	\hfill \emph{Email:} \href{mailto:sgrover@gatech.edu}{sgrover@gatech.edu}\\
    Atlanta, GA		\hfill \emph{Web:} \href{http://gtnoise.net/~sarthak}{gtnoise.net/{\tiny$\sim$}sarthak}	\\\vspace{-4.5mm}

    %__________________________________________________________________________________________________________________
    % Objective
    %\section{\mysidestyle Objective}

    %Admission to a top graduate school for doctoral studies and world-class research
    %in the field of Wireless Communication and Networking


    %__________________________________________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle \normalsize Research\\Interests}

    Wireless Performance Analysis, Home Network Security, Software Defined Networking, Internet of Things, Network Measurement

    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle \normalsize Education}

    \textbf{Georgia Institute of Technology (GaTech)}  		\hfill \textbf{2012  Onwards} \\%\vspace{2mm}\\\vspace{-2mm}%
    \emph {Ph.D in Computer Science with Major in Networking and Communications}			 \\\vspace{-4mm}
    \begin{list2}
      \item Advisor: \href{http://www.cc.gatech.edu/~feamster/}{Prof. Nick Feamster}
      \item CGPA: 3.871/4.00 (Current)
    \end{list2}
    
    \textbf{Indian Institute of Technology (IIT) Roorkee, India}  		\hfill \textbf{2005 -- 2010} \\%\vspace{2mm}\\\vspace{-2mm}%
    \emph {B. Tech, Electronics and Communication Engineering \& M. Tech, Wireless Communication}			 \\\vspace{-4mm}
    \begin{list2}
      \item Dissertation: Performance Evaluation of WBAN using Cross Layer Approach
      \item CGPA: 8.062/10.00 (India)
    \end{list2}

    %__________________________________________________________________________________________________________________
    % Test Scores
    %\section{\mysidestyle \normalsize Test Scores}
    %\textbf{GRE:} 1420/1600 (V: 640, Q: 780, A: 4.5);
    %\textbf{iBT TOEFL:} 116/120 (R: 29, L: 29, S: 29, W: 29)
    %__________________________________________________________________________________________________________________
    % Publications
    \section{\mysidestyle \normalsize Publications}

    B. Jones, S. Burnett, N. Feamster, S. Donovan, \textbf{S. Grover}, S. Gunasekaran, K. Habak,
    ``Facade: High-Throughput, Deniable Censorship Circumvention Using Web Search'', Submitted to
    \emph{USENIX Workshop on Free and Open Communications on the Internet (FOCI)}, August 2014.

\vspace{-2.5mm}
    M. S. Seddiki, M. Shahbaz, S. Donovan, \textbf{S. Grover}, M. Park, N. Feamster, Y. Song,
    ``FlowQoS: QoS for the Rest of Us'',
    \emph{ACM SIGCOMM 2014 Workshop on Hot Topics in Software Defined Networking (HotSDN)}, Poster and Demonstration, August 2014.

\vspace{-2.5mm}
    \textbf{S. Grover}, M. Park, S. Sundaresan, S. Burnett, H. Kim,
    N. Feamster,
    ``\href{http://dx.doi.org/10.1145/2504730.2504736}
    {Peeking Behind the NAT: An Empirical Study of Home Networks}'',
    \emph{ACM SIGCOMM Internet Measurement Conference (IMC)}, October 2013.

\vspace{-2.5mm}
    \textbf{S. Grover}, N. Feamster,
    ``Panoptes: Detecting Malware Activity in Home Networks'',
    \emph{HomeSys: Workshop on Design, Technology, Systems
    and Applications for the Home (UbiComp)}, Poster and Demonstration,
    September 2013.

\vspace{-2.5mm}
    A. Gupta, \textbf{S. Grover},
    ``\href{https://www.usenix.org/system/files/nsdip13-paper45.pdf}
    {mPaaS: Delivering Mobile Platforms as a Cloud Service}'',
    \emph{USENIX Symposium on Networked Systems Design and Implementation (NSDI)}, Poster and Demonstration, April 2013.

\vspace{-2.5mm}    
    V. Sivaraman, A. Dhamdhere, H. Chen, A. Kurusingal, \textbf{S. Grover},
    ``\href{http://www.sciencedirect.com/science/article/pii/S1570870512001631}
    {An Experimental Study of Wireless Connectivity and Routing in Ad-hoc
    Sensor Networks for Real-Time Soccer Player Monitoring}",
    \emph{Ad Hoc Networks (Elsevier)}, Vol. 11 Issue 3, pp.798-817, May 2013.
    
\vspace{-2.5mm}
    V. Sivaraman, \textbf{S. Grover}, A. Kurusingal, A. Dhamdhere, A. Burdett,
    ``\href{http://dx.doi.org/10.1109/WIMOB.2010.5645046}
    {Experimental Study of Mobility in the Soccer Field with Application
    to Real-Time Athlete Monitoring}'',
    \emph{Proceedings of IEEE Wireless \& Mobile Computing, Networking and
    Communications (WiMob)}, pp.337-345, November 2010.
    \textbf{(Best Paper Award)}

\vspace{-2.5mm}
    \textbf{S. Grover},
    ``\href{https://docs.google.com/open?id=0BysO4IvPeA4SMjQ5N2MzZWMtNjYxNC00MzA5LWI0ODUtODdlMjFkZWMzNDBm}
    {Performance Evaluation of Wireless Body Area Network using Cross Layer Approach}'',
    \emph{Master's Thesis}, Indian Institute of Technology Roorkee, June 2010.

\vspace{-2.5mm}
    V. Saxena, \textbf{S. Grover}, S. Joshi,
    ``\href{http://dx.doi.org/10.1109/UKRICIS.2008.4798956}
    {A Real Time Face Tracking System using Rank Deficient Face Detection and Motion Estimation}'',
    \emph{Proceedings of IEEE Cybernetic Intelligent Systems (CIS)}, pp.1-6,
    September 2008.
    % http://dx.doi.org/10.1109/UKRICIS.2008.4798956

    %__________________________________________________________________________________________________________________
    % Academic Positions
    \section{\mysidestyle \normalsize Academic\\Positions}
    \textbf{Research Engineer} at \emph{Laboratoire d’Informatique de Paris 6,} UPMC 	\hfill \textbf{May 2014 -- Aug 2014} \\\vspace{-4mm}
    \begin{list2}
    \item Home network diagnosis for performance bottleneck detection;
    \end{list2}
\vspace{-1.5mm}

    \textbf{Teaching Assistant}  at \emph{School of Computer Science,} Georgia Tech\\
    \emph{CS3251: Computer Networks}						\hfill \textbf{Fall 2013}\\\vspace{-4mm}
    \begin{list2}
    \item Creating and grading assignments, conducting TA hours;
    \end{list2}
    
    \textbf{Research Engineer} at \emph{Laboratoire d’Informatique de Paris 6,} UPMC 	\hfill \textbf{Jun 2013 -- Sep 2013} \\\vspace{-4mm}
    \begin{list2}
    \item Home network measurement to create a troubleshooting platform using Fathom and BISmark;
    \end{list2}
\vspace{-1.5mm}

    \textbf{Graduate Research Assistant} at \emph{School of CS,} Georgia Tech		\hfill \textbf{Aug 2012 Onward} \\\vspace{-4mm}
    \begin{list2}
    \item QoS control using SDN for home networks;
    \item HTTP Pluggable transport protocols to avoid censorship and detection for Tor;
    \item Analysis of home network availability, infrastructure, and traffic using BISmark;
    \item Home network security from the point of view of a gateway by detecting malware in Internet traffic;
    \item End-to-end routing in the Internet and broadband performance analysis using BISmark;
    \end{list2}
\vspace{-1.5mm}

    \textbf{Visiting Research Scholar} at \emph{Department of CS,} NC State University		\hfill \textbf{Jan 2012 -- Mar 2012} \\\vspace{-4mm}
    \begin{list2}
    \item Indoor Localization for Samsung and wireless network system design and implementation;
    \end{list2}
\vspace{-1.5mm}

    \textbf{Junior Research Fellow} at \emph{Department of ECE,} IISc Bangalore				\hfill \textbf{Mar 2011 -- Dec 2011}		\\
    \emph{Indo-Brazil WINSON Project} 				 			\\\vspace{-4mm}
    \begin{list2}
    \item Research on wireless sensor networks for societal needs and disaster management;
    prepared work-plan proposal for submission to the Department of Science and Technology (DST), Govt of India;
    \end{list2}
\vspace{-3mm}

    \emph{SmartConnect: DIT-ASTEC WSN Project}					\\\vspace{-4mm}
    \begin{list2}
    \item Deployment of industrial wireless sensor networks, project demonstrations and experimental data analysis;
    \end{list2}
\vspace{-1.5mm}

    \textbf{Teaching Assistant}  at \emph{Department of ECE,} IIT Roorkee		\\
    \emph{EC311: Principles of Digital Communication}		\hfill \textbf{Fall 2009}\\
    \emph{EC102: Fundamentals of Electronics} 			\hfill \textbf{Spring 2010}\\\vspace{-4mm}
    \begin{list2}
    \item Teaching beginner level digital communication to a class of 25 students;
    \item Preparing assignments, conducting tutorial classes, creating and grading examination papers;
%Responsibilities included teaching certain topics, preparing assignments,
%conducting tutorial classes, invigilating examinations and grading exam papers
    \end{list2}

    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle \normalsize Professional\\Experience}
 	\begin{list2}
     \item Summer Intern at \textbf{University of New South Wales}, Sydney, Australia under  \emph{Prof. Vijay Sivaraman} \\
    \emph{Wireless Body Area Networks for Athlete Monitoring} \hfill\textbf{May 2009 -- Aug 2009}\\\vspace{-4mm}
    \item Summer Intern at \textbf{Aricent Technologies Ltd.}, Gurgaon, India under \emph{Mr. Mandeep S. Bedi} \\
    \emph{Alarm Handling for Nokia Epsilon Flexi EDGE Base Transceiver System (BTS)} \hfill \textbf{May 2008 -- Jul 2008}\\
  	\end{list2}
  	
    %__________________________________________________________________________________________________________________
    % Research Projects
    \section{\mysidestyle \normalsize Research\\Projects}
    
\textbf{FlowQoS: Providing Per-Flow Quality of Service for Broadband Access Networks}
    \emph{(\href{http://gtnoise.net/}{GTNoise})} \\
    \hspace{-1pt}\emph{Advisor: {Nick Feamster}}
    \emph{(School of CS, Georgia Institute of Technology)}			\hfill \textbf{Jan 2013} \\
    \hspace{-1pt}\emph{\href{http://flowqos.noise.gatech.edu/}{FlowQoS}/CS 8001: Software Defined Networking} 		\\\vspace{-4mm}
    %description of project
    \begin{list2}
    \item Designed an SDN based system to allocate QoS based on application and devices in a home network. My main contribution was the DNS based flow classifier, which forwards traffic through appropriate traffic shapers in a home router.
    \item Results published at HotSDN 2014, Chicago, IL.
    \end{list2}
\vspace{-2mm}

\textbf{Facade: High-Throughput, Deniable Censorship Circumvention Using Web Search}
    \emph{(\href{http://gtnoise.net/}{GTNoise})} \\
    \hspace{-1pt}\emph{Advisor: {Nick Feamster}}
    \emph{(School of CS, Georgia Institute of Technology)}			\hfill \textbf{Jan 2013} \\
    \hspace{-1pt}\emph{CS 6250: Computer Networks} 		\\\vspace{-4mm}
    %description of project
    \begin{list2}
    \item  Designed and implemented a new encoding technique that uses web search terms to encode hidden messages in an upstream channel for censorship circumvention to resist fingerprinting attacks.
    \item Results published at FOCI 2014, San Diego, CA.
    \end{list2}
\vspace{-2mm}

    \textbf{Browserlab: Home Network Diagnosis and Bottleneck Detection}
    \emph{(\href{http://www.lip6.fr/}{LIP6})} \\
    \hspace{-1pt}\emph{Advisor: \href{http://www-npa.lip6.fr/~teixeira/}{Renata Teixeira}}
    \emph{(INRIA, University Pierre and Marie Curie)}
    \hfill \textbf{May 2013} \\
    \hspace{-1pt}\emph{\href{http://fathom.icsi.berkeley.edu/}{Fathom}/\href{http://projectbismark.net/}{BISmark}}		\\\vspace{-4mm}
    %description of project
    \begin{list2}
    \item Detect the performance bottleneck in a home network by collaborating between home devices. Created a monitoring system to collect detailed wireless measurements from synchronized devices in a home, and manage and upload this data to the centralized server for analysis.
	\item We develop the browserlab daemon that listens on multiple network devices in a home, and propose collaborative bottleneck detection algorithm to identify if the access link is the bottleneck or the wireless is. Next, the daemon will be ported as a browser extension to scale the solution and collect large scale home wireless measurements.
    %\item Integrating and extending the Fathom and BISmark measurement platforms to develop a home network troubleshooter for internal and external network diagnosis. The API allows a user to communicate between connected clients, and with the gateway, to issue parallel tests to analyse the home networks performance.
    \end{list2}
\vspace{-2mm}

    \textbf{Performance Analysis of Home Broadband Networks}
    \emph{(\href{http://gtnoise.net/}{GTNoise})} \\
    \hspace{-1pt}\emph{Advisor: {Nick Feamster}}
    \emph{(School of CS, Georgia Institute of Technology)}			\hfill \textbf{Jan 2013} \\
    \hspace{-1pt}\emph{\href{http://projectbismark.net/}{Project BISmark}} 		\\\vspace{-4mm}
    %description of project
    \begin{list2}
    \item Empirical study and analysis of availability, infrastructure, and usage of home broadband networks based on active and passive measurement data collected from the BISmark gateways. First large scale measurement and analysis work which provides us a view of home networks behind the NAT and discusses the differences observed in kind of devices used, and the distribution of usage with time, in developed and developing countries.
    \item Results published at ACM SIGCOMM IMC 2013, Barcelona, Spain.
    \end{list2}
\vspace{-2mm}

    \textbf{SAZO: Constant Guard for Home Network Security}
    \emph{(\href{http://gtnoise.net/}{GTNoise})} \\
    \hspace{-1pt}\emph{Advisor: {Nick Feamster}}
    \emph{(School of CS, Georgia Institute of Technology)}			\hfill \textbf{Jan 2013} \\
    \hspace{-1pt}\emph{Comcast} 		\\\vspace{-4mm}
    %description of project
    \begin{list2}
    \item Proposed that security management of home networks be outsourced to an expert third party. Extended BISmark's passive monitoring capability to monitor customer traffic for suspicious activity from specific network devices. On detecting suspicious traffic, the traffic is automatically redirected through Comcast's VPN for security analysis and the home owner is notified.
    \item Preliminary work presented as a poster at the Homesys '13 workshop, Ubicomp.
    \end{list2}
\vspace{-2mm}

    \textbf{End-to-end Routing Behavior in the Internet: A Re-Appraisal from Access Networks}
    \emph{(\href{http://gtnoise.net/}{GTNoise})} \\
    \hspace{-1pt}\emph{Advisor: {Nick Feamster}}
    \emph{(School of CS, Georgia Institute of Technology)}			\hfill \textbf{Aug 2012} \\
    \hspace{-1pt}\emph{\href{http://projectbismark.net/}{Project BISmark}} 		\\\vspace{-4mm}
    %description of project
    \begin{list2}
    \item Analyzed traceroute data from access networks to a variety of Internet destinations and examined route persistence and prevalence. Our aim is to associate home network performance metrics with path changes due to traffic engineering policies.
    \item Preliminary results were presented in a talk at Active Internet Measurement Symposium (AIMS), CAIDA.
    \end{list2}
\vspace{-2mm}

    \textbf{Indoor Localization using FM}  \emph{(\href{http://research.csc.ncsu.edu/netsrv/}{Networking Research Lab})} \\
    \hspace{-1pt}\emph{Advisor: \href{http://www4.ncsu.edu/~rhee/}{Prof. Injong Rhee}}
    \emph{(Department of CS, North Carolina State University)}			\hfill \textbf{Jan 2012} \\
    \hspace{-1pt}\emph{Samsung Localization Project} 		\\\vspace{-4mm}
    %description of project
    \begin{list2}
    \item Implemented FM/AM transmitter and receiver systems using GNURadio. Aim is to utilize RDS information and track stereo component to enable indoor localization of SmartPhones.
    \end{list2}
\vspace{-2mm}

    \textbf{Design of Multi-Hop Wireless Networks for In-Hospital Applications} \emph{(\href{http://www.ece.iisc.ernet.in/network_labs/netarch.html}
    {Network Architecture Lab})} \\
    \hspace{-1pt}\emph{Advisor: \href{http://www.ece.iisc.ernet.in/~anurag/index.htm}{Prof. Anurag Kumar}
    (Chairman, Electrical Sciences Div., IISc Bangalore)}		\hfill \textbf{Mar 2011} \\
    \hspace{-1pt}\emph{Indo-Brazil WINSON Project funded by DST, Govt. of India} 		\\\vspace{-4mm}
    %description of project
    \begin{list2}
    \item Computed closed form expressions for network reliability in hexagonal (lattice) hybrid wireless networks
    with link failures and fading. Proposed tier-rank based routing protocol. Evaluated information-theoretic bounds 
    for random hybrid networks (Poisson RGG).
    \item Applications include mobile patients and equipment tracking and sensing, home health
    care, baby monitoring, electronic boarding passes, and lost child tracking.
    \emph{(Work on publication in progress)}
    \end{list2}
\vspace{-2mm}

    \textbf{Performance Evaluation of a Wireless Body Area Network}
    \emph{(\href{http://www.iitr.ac.in/departments/ECE/pages/Research+Facilities+labs+Network_Security.html}
    {Network Security Lab})}  							\\
    \emph{Advisor: \href{http://www.iitr.ac.in/~ECE/scecefec}{Mr. S. Chakravorty}
    (Department of ECE, IIT Roorkee)} \hfill \textbf{Aug 2009} 	\\
    \emph{Dual Degree project for submission of Master's Dissertation}	\\\vspace{-4mm}
    \begin{list2}
    \item Implemented cross layer protocol to auto-regressively predict PHY 
    parameters and control MAC level queue for mobile nodes in Rayleigh fading environment.
    Modeled human body channel for intra BAN (on-body network). Comprehensive
    simulations on NS2 showed improved network throughput and lifetime.
    \item Applications include energy efficient athlete monitoring and remote health care for mobile users.
    \end{list2}
\vspace{-2mm}

    \textbf{Implementation of a Soft Decision Decoder using Trellis on FPGA}
    \emph{(\href{http://www.iitr.ac.in/departments/ECE/pages/Research+Facilities+labs+Singnal_Processing.html}
    {Signal Processing Lab})}   						\\
    \hspace{-1pt}\emph{Advisor: Mr. S. Chakravorty (Department of ECE, IIT Roorkee)}	\hfill \textbf{Aug 2009} 	\\\vspace{-4mm}
    %description of project
    \begin{list2}
    \item Implemented a real-time trellis decoder for BCH codes using VHDL on Xilinx ISE and configured it on FPGA.
    Dedicated hardware was shown to achieve higher data rate compared to software implementation.
    \end{list2}
\vspace{-2mm}

    \textbf{Wireless Body Area Networks for Athlete Monitoring}
    \emph{(\href{http://www.eet.unsw.edu.au/}{School of EE\&T})}					\\
    \hspace{-1pt}\emph{Advisor: \href{http://www2.ee.unsw.edu.au/~vijay/}{Dr. Vijay Sivaraman}
    (University of New South Wales, Sydney)} 			\hfill \textbf{May 2009} 	\\
    \emph{Collaboration with Toumaz Technology Ltd., U.K.} 		 \\\vspace{-4mm}
    %description of project
    \begin{list2}
    \item Monitored inter-connectivity between players using wireless bio-medical sensors and
    multiple base stations during soccer games. Analyzed time-series experimental data
    and developed encounter based model to capture user mobility, and generate synthetic network topologies.
    Simulated encounter based real-time routing scheme for dynamic multi-hop networks.
    Applications include providing referee-assist and enhanced television broadcast services during games.
    \item Awarded the best student paper at \emph{IEEE WiMob 2010}, Niagara Falls, Canada (Acceptance: 28.9).
    \end{list2}
\vspace{-2mm}

    \textbf{Real Time Human Face Tracking System}
    \emph{(\href{http://www.iitr.ac.in/campus_life/pages/Clubs+Hobbies_Club+Electronics.html}
    {Electronics Section})}  								\\
    \emph{Student Project, Annual Hobbies Club Exhibition
    `Sristi', IIT Roorkee} 				\hfill \textbf{Dec 2007 -- Mar 2008} 	\\\vspace{-4mm}
    %description of project
    \begin{list2}
    \item Developed a robust real-time face tracking algorithm using rank deficient face detection
    to iteratively search and track the human face in each video frame. 
    Demonstrated the system by mounting camera on robotic arm.
    Potential applications include focusing on speaker
    during conferences, and recording lectures.
    \item Results published in proceedings of \emph{IEEE CIS 2008}. Demonstration awarded first prize at \emph{`Sristi'}.
    \end{list2}
% \vspace{-2mm}
%
%     \textbf{Design of Circular Patch Microstrip Antenna}
%     \emph{(\href{http://www.iitr.ac.in/departments/ECE/pages/Research+Facilities+labs+Advanced_Microwave_Laboratory.html}
%     {Advanced Microwave Lab}})  						\\
%     \emph{Guide: \href{http://www.iitr.ac.in/~ECE/apfecfec}{Dr. Amalendu Patnaik}
%     (Department of ECE, IIT Roorkee)} \hfill \textbf{Sep 2007 -- Dec 2007} 	\\\vspace{-4mm}
%     %description of project
%     \begin{list2}
%     \item Optimized dimensions of Circular Patch Microstrip Antenna using Particle
%     Swarm Optimization (PSO). Results indicated better speed and accuracy in comparison
%     to genetic algorithm (GA) approach.
%     \end{list2}

    %__________________________________________________________________________________________________________________
    % Workshops
% Indian Institute of Science,
% University of New South Wales
% Indian Institute of Technology
%    \section{\mysidestyle \normalsize Conferences}
%    \textbf{NSDI}, USENIX, Lombard, IL, April 2013 		\vspace{0.5mm}\\
%    \textbf{AIMS-5}, CAIDA, San Diego, CA, February 2013 		\vspace{0.5mm}\\
%    \textbf{IMC}, ACM SIGCOMM and SIGMETRICS, Boston, MA, November 2012 		\vspace{0.5mm}\\
%    \textbf{Google DevFest}, Bangalore, September 2011 		\vspace{0.5mm}\\
%    \textbf{Introduction to Network Science}, IMI Workshop, IISc Bangalore,
%    August 2011 								\vspace{0.5mm}\\
%    \textbf{Inside an Internet Router}, NICTA Workshop, UNSW Sydney,
%    June 2009								\vspace{0.5mm}\\
%    \textbf{Motorola Summit}, IEEE Workshop, IIT Roorkee,
%    September 2007
%
    %__________________________________________________________________________________________________________________
    % Relevant Courses
% 
%     \section{\mysidestyle \normalsize Relevant\\Courses}
% 
%     \textbf{Communication and Networking:} Wireless Networks; Coding Theory \& Applications; Information \& Communication Theory;
%     Advanced Digital Communication; Telecommunication Networks; Wireless Communication Links \& Antennas;
%     Computer Networks; Communication Systems \& Techniques; Adaptive Signal Processing; \\
%     Others: Modeling and Simulation; Numerical Methods; Fuzzy sets \& systems; Mathematics I,II, \& III consisting of
%     Probability and Stochastic Processes, Complex Variables, Transform Techniques, Vectors Matrices;

    %__________________________________________________________________________________________________________________
    % Technical Skills
    \section{\mysidestyle \normalsize Technical\\Skills}
    \textbf{Languages:} Python, C/C++, JavaScript, VHDL, Tcl/Tk, Assembly 8085/8086, HTML,
    CSS, VBScript							\vspace{1mm}\\
    \textbf{Platforms:} Openwrt, Node.js, iPython, GNURadio, MATLAB, NS-2, TinyOS,
    Xilinx ISE, GPSS							\vspace{1mm}\\
    Others: Unix, Adobe Photoshop, Corel Draw, Adobe Flash, Dreamweaver, MS Office, \LaTeX

    %__________________________________________________________________________________________________________________
    % Honors and Awards
    \section{\mysidestyle \normalsize Honors and\\Awards}

    \textbf{Graduate Research Assistantship} at GaTech \hfill \textbf{Aug 2012 Onwards}\vspace{0mm}\\
    \textbf{Research Fellowship} at NCSU	\hfill \textbf{Jan 2012 -- Mar 2012}\vspace{0mm}\\
    \textbf{Research Fellowship} at IISc, Bangalore	\hfill \textbf{Mar 2011 -- Dec 2011}\vspace{0mm}\\
    \textbf{Best Student Paper Award} at IEEE WiMob 2010	 \hfill \textbf{Oct 2010}\vspace{0mm}\\
    \textbf{Half-Time Teaching Assistant Scholarship} at IIT Roorkee		 \hfill \textbf{Aug 2009 -- Jun 2010}\vspace{0mm}\\
    \textbf{Student Exchange Program Scholarship} at UNSW, Sydney	\hfill \textbf{May 2009 -- Aug 2009}\vspace{0mm}\\
    Awarded \textbf{First Prize} at Annual Hobbies Club Exhibition, IIT Roorkee	\hfill \textbf{Mar 2008}\vspace{0mm}\\
    \textbf{14th position} at National Mathematical Olympiad (Delhi)	 \hfill	\textbf{Feb 2004}
    %\item Secured an All India Rank of 1195 (99.99 percentile) in the National Level Science Talent Search Examination (NSTSE-2002) conducted by the Unified Council
    %\item Secured an All India Rank of 1081 (99.99 percentile) in Joint Entrance Exam, Indian Institute of Technology (IIT JEE 2005)

    %__________________________________________________________________________________________________________________
    % Extra-Curricular
%    \section{\mysidestyle \normalsize Positions of\\Responsibility}
%
%    \textbf{IEEE Student Chapter}				\hfill \textbf{2006 -- 2010}\\\vspace{-4mm}
%    \begin{list2}
%    \item \emph{Treasurer} for session '08--'09
%    \item \emph{Founder and Chief Designer} of `GeekGazette', institute's first technical magazine
%    \item \emph{Member} of IEEE since 2006
%    \end{list2}
%\vspace{-4mm}
%
%    \textbf{Watch Out News Agency}				\hfill \textbf{2005 -- 2008}\\\vspace{-4mm}
%    \begin{list2}
%    \item \emph{Chief Designer} of `Watch Out', institute's news magazine
%    \end{list2}
%\vspace{-4mm}
%
%    \textbf{Others}						\hfill \textbf{2006 -- 2008}\\\vspace{-4mm}
%    \begin{list2}
%    \item \emph{Cognizance (Annual Technical Fest):} Design Coordinator; Co-coordinator, mega quizzing event
%    \item \emph{Thomso (Annual Cultural Fest):} Coordinator, center stage event; Organizer, virtual gaming fest
%    \end{list2}

%     \textbf{Thomso: Annual Cultural Festival, IIT Roorkee}			\hfill \textbf{2006 -- 2007}\\\vspace{-4mm}
%     \begin{list2}
%     \item \emph{Coordinator,} center stage event `Mr \& Ms Thomso'; 		 \hfill 2007
%     \item \emph{Organizer,} `Apocalypse', virtual gaming fest			 \hfill 2006
%     \end{list2}
% \vspace{-4mm}
%
%     \textbf{Cognizance: Annual Technical Festival, IIT Roorkee}			\hfill \textbf{2006 -- 2007}\\\vspace{-4mm}
%     \begin{list2}
%     \item \emph{Design Coordinator}						 	\hfill 2007
%     \item \emph{Co-coordinator} of mega quizzing event				 \hfill 2006
%     \end{list2}

    %__________________________________________________________________________________________________________________
    % Referees
    \section{\mysidestyle \normalsize References}
    {\sl Available on request. \vspace{-4mm}}

    %__________________________________________________________________________________________________________________
    % Please see my website
%    \section{}
    \centering
      \small For more information and details, please visit my website
    \href{http://gtnoise.net/~sarthak}{http://gtnoise.net/{\tiny$\sim$}sarthak}
    %resume link: https://sites.google.com/site/shahifaqeer/cv/resume
%______________________________________________________________________________________________________________________
%\section{\mysidestyle Referees}

%\begin{tabular}{@{}p{6cm}p{6cm}}
%\textbf{Professor Kuldip Paliwal}       &  \textbf{Dr Stephen So}                   \\
%Professor                               &  Associate Lecturer                       \\
%Griffith University                     &  Griffith University                      \\
%Nathan, Queensland, Australia           &  Gold Coast, Queensland, Australia        \\
%phone: \emph{available on request}    &  phone: \emph{available on request}     \\
%e-mail: \emph{available on request}   &  e-mail: \emph{available on request}    \\
%\end{tabular}
%
%\begin{tabular}{@{}p{6cm}p{6cm}}
%\textbf{Dr Conrad Sanderson}            &  \textbf{Mr Sean Loye}                    \\
%Researcher                              &  Systems Engineer                         \\
%National ICT Australia                  &  Hewlett Packard                          \\
%St Lucia, Queensland, Australia         &  Milton, Queensland, Australia            \\
%phone: \emph{available on request}    &  phone: \emph{available on request}     \\
%e-mail: \emph{available on request}   &  e-mail: \emph{available on request}    \\
%\end{tabular}
%______________________________________________________________________________________________________________________
\end{resume}
\end{document}

%______________________________________________________________________________________________________________________
% EOF